Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-08 free_boson_lattice.tex
[draft] fix reference error

To find the scattering matrix, we set up the plane wave scattering problem across the interface using ansatz for two semi-infinite chain (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
\begin{equation}
\label{eq:ansatz}
\phi_n
= \left\lbrace
  \begin{aligned}
    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
  \end{aligned} \right. 
 \quad 
\end{equation}
where $a$ is the lattice constant. The dispersion of the system is $\omega = \left|2\sin\frac{k}{2}\right|$ which implies the system is gapless. The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}. Upon plugging Eq.~\eqref{eq:ansatz}-\eqref{eq:dispersion} into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
\begin{equation}
\label{eq:discrete_S}
\begin{pmatrix}
A_{-} \\
B_{+}\\
\end{pmatrix}
=-
\begin{bmatrix}
\Sigma_{11} + e^{-ika} & \Sigma_{12} \\
\Sigma_{21} & \Sigma_{22}  + e^{-ika}  \\
\end{bmatrix}^{-1}
\begin{bmatrix}
\Sigma_{11} +e^{ika} & \Sigma_{12}\\
\Sigma_{21} & \Sigma_{22} + e^{ika}
\end{bmatrix}
\begin{pmatrix}
A_{+}\\
B_{-}\\
\end{pmatrix}
\end{equation}
and the scattering matrix can be solved as
\begin{equation}
  S = \frac{-1}{ \det \Sigma  + e^{-ika} \text{tr} \Sigma   + e^{-2ika}}
\begin{bmatrix}
\det \Sigma+ \Sigma_{11} e^{-ika} + \Sigma_{22} e^{ika}+1  & -2i \sin ka \Sigma_{12}  \\
-2i \sin ka \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ika} + \Sigma_{22} e^{-ika}+1\\
\end{bmatrix}
\end{equation}
A necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
\begin{equation}
\label{eq:Sigma_condition}
\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
\end{equation}
Therefore, we have the scale invariant S-matrix as
\begin{equation}
S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
 = - e^{ika} \Sigma
\end{equation}
In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
\begin{equation}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
in accordance to Eq.~\eqref{eq:Sigma_condition}.

>>>>

To find the scattering matrix, we set up the plane wave scattering problem across the interface using ansatz for two semi-infinite chain (the use of $(n-1)$ in $\phi_n^B$ simplifies the calculation)
\begin{equation}
\label{eq:ansatz}
\phi_n
= \left\lbrace
  \begin{aligned}
    \phi_n^A &= A_{-} e^{i \omega t  - inka}  + A_{+} e^{i \omega t  + inka}  & \quad  n \le 0 \\
    \phi_n^B &= B_{-} e^{i \omega t  - i(n-1)ka}  + B_{+} e^{i \omega t  + i(n-1)ka} & \quad n \ge 1 \\
  \end{aligned} \right. 
 \quad 
\end{equation}
where $a$ is the lattice constant. The dispersion of the system is $\omega = \left|2\sin\frac{k}{2}\right|$ which implies the system is gapless. The interface will not break the criticality of the harmonic chain\cite{peschel_exact_2012}. Upon plugging ansatz and dispersion relation into the equation of motion, we have the following relation between the incoming and outgoing amplitudes
\begin{equation}
\label{eq:discrete_S}
\begin{pmatrix}
A_{-} \\
B_{+}\\
\end{pmatrix}
=-
\begin{bmatrix}
\Sigma_{11} + e^{-ika} & \Sigma_{12} \\
\Sigma_{21} & \Sigma_{22}  + e^{-ika}  \\
\end{bmatrix}^{-1}
\begin{bmatrix}
\Sigma_{11} +e^{ika} & \Sigma_{12}\\
\Sigma_{21} & \Sigma_{22} + e^{ika}
\end{bmatrix}
\begin{pmatrix}
A_{+}\\
B_{-}\\
\end{pmatrix}
\end{equation}
and the scattering matrix can be solved as
\begin{equation}
  S = \frac{-1}{ \det \Sigma  + e^{-ika} \text{tr} \Sigma   + e^{-2ika}}
\begin{bmatrix}
\det \Sigma+ \Sigma_{11} e^{-ika} + \Sigma_{22} e^{ika}+1  & -2i \sin ka \Sigma_{12}  \\
-2i \sin ka \Sigma_{21} &  \det \Sigma+ \Sigma_{11} e^{ika} + \Sigma_{22} e^{-ika}+1\\
\end{bmatrix}
\end{equation}
A necessary condition for the scattering matrix to be scale invariance is that the ratio $|S_{11}/S_{21}|$ is independent of $k$. This implies 
\begin{equation}
\label{eq:Sigma_condition}
\det \Sigma = -1, \, \, \text{tr} \Sigma = 0
\end{equation}
Therefore, we have the scale invariant S-matrix as
\begin{equation}
S = \frac{1}{1 - e^{-2ika } } ( -2i \sin k ) \Sigma
 = - e^{ika} \Sigma
\end{equation}
In the continuum limit where $a\rightarrow0$, the matrix $\Sigma$ can be parameterized as
\begin{equation}
\Sigma = -\lim_{a \rightarrow 0 } S = 
\begin{bmatrix}
\frac{\lambda^2- 1}{1 + \lambda^2} & \frac{-2\lambda }{1 + \lambda^2} \\
\frac{-2\lambda }{1 + \lambda^2} & \frac{1- \lambda^2}{1 + \lambda^2} \\
\end{bmatrix}
\end{equation}
in accordance to Eq.~\eqref{eq:Sigma_condition}.
